The ordertrans() function

### 2021-01-16 inst/ordertrans.Rmd
typos

In the above, object `x` is a named vector with elements
\code{seq_along(x)} in some order.  Technically `x` is an order vector
because it answers the question "where did the first-named competitor
come?"  (see also the discussion at `rrank.Rd`).  However, it might
equally be a rank vector because it answers the question "who came
first? who came second?".

@@

So now we may compare judge 1 against likelihood:
```{r,transplotjudge1}
ordertransplot(mL,j1,xlab="likelihood rank",ylab="Judge 1 rank")
```

>>>>

In the above, object `x` is a named vector with elements
`seq_along(x)` in some order.  Technically `x` is an order vector
because it answers the question "where did the first-named competitor
come?"  (see also the discussion at `rrank.Rd`).  However, it might
equally be a rank vector because it answers the question "who came
first? who came second?".

@@

So now we may compare judge 1 against likelihood:

```{r,transplotjudge1}
ordertransplot(mL,j1,xlab="likelihood rank",ylab="Judge 1 rank")
```
